\documentclass[../constitution.tex]{subfiles}
\begin{document}

\nonnumberedparts{Own rules matters}

To assist with the completion of \href{https://www.commerce.wa.gov.au/publications/notice-special-resolution-change-rules}{\textit{Form 5 - Notice of special resolution to change rules}}, this section provides a correspondence between:

\begin{itemize}
    \item Schedule 1 of the Act --- \textit{Matters to be provided for in rules of an incorporated association}; and
    \item The relevant sections of these rules.
\end{itemize}

The text below is exactly reproduced from the Act (as at 01 Jul 2016), which varies from the text of Form 5 in minor details.

\section*{Division 1 — Matters to be addressed}

 {\def\arraystretch{1.3}
  \begin{xltabular}{\textwidth}{ |X|X| }
      \hline
      1. The name of the incorporated association.
      &
      Key Information - Item \ref{key-info-name-of-association}
      \\


      \hline
      2. The objects or purposes of the incorporated association.
      &
      Key Information - Item \ref{key-info-objects-purposes}
      \\


      \hline
      3. The qualifications (if any) for membership of the incorporated association and provision for when membership commences and when it ceases.
      &
      Part \ref{part-3-members}, Div \ref{division-1-membership}, s\ref{applying-for-membership} --- \ref{when-membership-ceases}
      \\


      \hline
      4. The register of members of the incorporated association.
      &
      Part \ref{part-3-members}, Div \ref{division-3-register-of-members}, s\ref{register-of-members}
      \\


      \hline
      5. The entrance fees, subscriptions and other amounts (if any) to be paid by members of the incorporated association.
      &
      Part \ref{part-3-members}, Div \ref{division-2-membership-fees}, s\ref{membership-fees}
      \\


      \hline
      6. The name, constitution, membership and powers of the management committee or other body having the management of the incorporated association (in this clause referred to as the committee) and provision for the following —
      &
      Part \ref{part-5-committee}.

      Name of governing body: "management committee" - refer Div \ref{division-1-powers-of-committee}, s\ref{committee}.

      Powers of committee: refer Div \ref{division-1-powers-of-committee}, s\ref{committee}.

      Constitution (composition) of management committee: refer Div \ref{division-2-composition-of-committee-and-duties-of-members}, s\ref{committee-members} --- \ref{treasurer}
      \\


      \hline
      (a) the election or appointment of members of the committee;
      &
      Part \ref{part-5-committee}, Div\ref{division-3-election-of-committee-members-and-tenure-of-office}, s\ref{how-members-become-committee-members} --- s\ref{election-of-office-holders}
      \\


      \hline
      (b) the terms of office of members of the committee;
      &
      Part \ref{part-5-committee}, Div\ref{division-3-election-of-committee-members-and-tenure-of-office}, s\ref{term-of-office}
      \\


      \hline
      (c) the grounds on which, or reasons for which, the office of a member of the committee shall become vacant;
      &
      Part \ref{part-5-committee}, Div\ref{division-3-election-of-committee-members-and-tenure-of-office}, s\ref{resignation-and-removal-from-office} \& s\ref{when-membership-of-committee-ceases}
      \\


      \hline
      (d) the filling of casual vacancies occurring on the committee;
      &
      Part \ref{part-5-committee}, Div\ref{division-3-election-of-committee-members-and-tenure-of-office}, s\ref{filling-casual-vacancies}
      \\


      \hline
      (e) the quorum and procedure at meetings of the committee;
      &
      Quorum: Key Information - Item \ref{key-info-quorum-for-committee-meetings}

      Procedure at committee meetings: Part \ref{part-5-committee}, Div \ref{division-4-committee-meetings}
      \\


      \hline
      (f) the making and keeping of records of the proceedings at meetings of the committee;
      &
      Part \ref{part-5-committee}, Div \ref{division-4-committee-meetings}, s\ref{minutes-of-committee-meetings}
      \\


      \hline
      (g) subject to Division 2 clause 1, the circumstances (if any) in which payment may be made to a member of the committee out of the funds of the association.
      &
      General expenses: Part \ref{part-2-association-to-be-not-for-profit-body}, s\ref{not-for-profit-body}

      Payments to committee members specifically: Part \ref{part-5-committee}, Div \ref{division-3-election-of-committee-members-and-tenure-of-office}, s\ref{payments-to-committee-members}

      Control of funds: Part \ref{part-7-financial-matters}, s\ref{control-of-funds}
      \\


      \hline
      7. The quorum and procedure at general meetings of members of the incorporated association.
      &
      Quorum: Key Information, Item \ref{key-info-quorum-for-general-meetings}

      Procedure at general meetings: Part \ref{part-6-general-meetings-of-association}, s\ref{proxies} --- s\ref{minutes-of-general-meeting}
      \\


      \hline
      8. The notification of members or classes of members of general meetings of the incorporated association and their rights to attend and vote at those meetings.
      &
      Part \ref{part-6-general-meetings-of-association}, s\ref{notice-of-general-meetings}
      \\


      \hline
      9. The time within which, and manner in which, notices of general meetings and notices of motion are to be given, published or circulated.
      &
      Part \ref{part-6-general-meetings-of-association}, s\ref{notice-of-general-meetings}
      \\


      \hline
      10. Subject to Division 2 clause 3, the number of members, expressed as a percentage of membership, who may at any time require that a general meeting of the incorporated association be convened.
      &
      Part \ref{part-6-general-meetings-of-association}, s\ref{special-general-meetings}
      \\


      \hline
      11. The manner in which the funds of the association are to be controlled.
      &
      Part \ref{part-7-financial-matters}, s\ref{control-of-funds}
      \\


      \hline
      12. Subject to Division 2 clauses 4 and 5, the day in each year on which the financial year of the incorporated association commences.
      &
      Key Information - Item \ref{key-info-financial-year}
      \\


      \hline
      13. The intervals between general meetings of members of the incorporated association and the manner of calling general meetings.
      &
      Part \ref{part-6-general-meetings-of-association}, s\ref{annual-general-meeting} --- s\ref{notice-of-general-meetings}
      \\


      \hline
      14. The manner of altering and rescinding the rules and of making additional rules of the incorporated association.
      &
      Part \ref{part-8-general-matters}, s\ref{alteration-of-rules}
      \\


      \hline
      15. Provisions for the custody and use of the common seal of the incorporated association, if it has one.
      &
      Part \ref{part-8-general-matters}, s\ref{no-common-seal}.
      \\


      \hline
      16. The custody of books and securities of the incorporated association.
      &
      Part \ref{part-8-general-matters}, s\ref{custody-of-books-and-securities}
      \\


      \hline
      17. The inspection by members of the incorporated association of records and documents of the incorporated association.
      &
      Part \ref{part-8-general-matters}, s\ref{inspection-of-records-and-documents}
      \\


      \hline
      18. A procedure for dealing with any dispute under or relating to the rules —
      (a) between members; or
      (b) between members and the incorporated association.
      &
      Part \ref{part-4-disciplinary-action-disputes-and-mediation}
      \\


      \hline
      19. Subject to section 24, the manner in which surplus property of the incorporated association must be distributed or dealt with if the association is wound up or its incorporation is cancelled.
      &
      Part \ref{part-8-general-matters}, s\ref{distribution-of-surplus-property-on-cancellation-of-incorporation-or-winding-up}
      \\


      \hline
      20.  A statement that the property and income of the association must be applied solely towards promoting the association's objects or purposes and no part of that property or income may be paid or otherwise distributed, directly or indirectly, to any member, except in good faith in promoting those objects or purposes.

      \bigskip

      \textit{This is an additional inclusion on Form 05 that is not in Schedule 1 of the Act.}
      &
      Part \ref{part-2-association-to-be-not-for-profit-body}, s\ref{not-for-profit-body}
      \\


      \hline
      21. The association's financial year will be the 12 month period ---

      \bigskip

      \textit{This is an additional inclusion on Form 05 that is not in Schedule 1 of the Act.}
      &
      starting from \textbf{1 July} to \textbf {30 June}.

      (As per Key Information - \ref{key-info-financial-year})
      \\


      \hline


  \end{xltabular}
 }

\pagebreak

\section*{Division 2 — Particular requirements for certain rules }


 {\def\arraystretch{1.3}
  \begin{xltabular}{\textwidth}{ |X|X| }

      \hline
      1. Payment to members of management committee

      \bigskip

      (1) Any rules made as mentioned in Division 1 item 6(g) are to provide
      for payment to be made to a member of the management committee of
      an incorporated association out of the funds of the association only if
      the payment is authorised by resolution of the association.

      \bigskip

      (2) Subclause (1) does not apply to payment to a member of the
      management committee for out-of-pocket expenses for travel and
      accommodation in connection with the performance of the member's
      functions.

      &

      Part \ref{part-2-association-to-be-not-for-profit-body}, s\ref{not-for-profit-body} states that the Association is a not-for-profit body, and provides that payments can be made to members (including committee members) for reimbursement of expenses and the like.

      \bigskip

      Part \ref{part-5-committee}, Div \ref{division-3-election-of-committee-members-and-tenure-of-office}, s\ref{payments-to-committee-members} specifies when payments can be made to committee members in connection with out-of-pocket expenses for travel and accommodation in connection with the performance of the member's functions.

      \bigskip

      There are no other provisions in the rules to make payments to committee members (\href{https://www.commerce.wa.gov.au/books/inc-guide-incorporated-associations-western-australia/paying-committee-members}{e.g. honorariums}) and thus there is no provision for such payments to be authorised by a resolution of the Association.

      \\

      \hline
      2. Entitlement of members in respect of general meetings

      \bigskip

      The rules made as mentioned in Division 1 item 8 must provide for all
      members of the incorporated association to be entitled to receive
      notice of and to attend any general meeting of the association.
      &

      Rule \ref{notice-of-general-meetings} requires that "each member" must be given notice of a general meeting. The definition of member in s\ref{terms-used} includes ordinary members and associate members, i.e. all members, regardless of their membership class or voting rights.

      \\

      \hline
      3. Number of members who may call a general meeting

      \bigskip

      The rules made for the purpose of Division 1 item 10 cannot specify
      greater than the prescribed percentage of members as the number of
      members who may at any time require that a general meeting be
      convened in accordance with the rules of the incorporated association.

      &

      Part \ref{part-6-general-meetings-of-association}, s\ref{special-general-meetings}, specifies that any 20\% of members may require a general meeting to be convened, which complies with the prescribed percentage in s18 of the Regulations.

      \\

      \hline
      4. Financial year of associations incorporated under this Act

      &

      N/A - association is not incorporated under the repealed Act.

      Note the financial year of the association is defined at Key Information - Item \ref{key-info-financial-year}

      \\

      \hline
      5. Transitional provisions as to financial year of associations
      incorporated under the repealed Act.

      &

      N/A - association is not incorporated under the repealed Act.

      \\

      \hline

  \end{xltabular}
 }

\end{document}