\documentclass[../constitution.tex]{subfiles}
\begin{document}

\part*{Key information} \label{key-information}

\begin{enumerate}[label=\Alph*.]
  \item \textbf{The name of the incorporated association:} \label{key-info-name-of-association}
  
  Perth Artifactory Inc.
  
  \item \textbf{The objects or purposes of the incorporated association:} \label{key-info-objects-purposes}
  


  \chdeleted[id=CAP3-Community-Shed]{The objects of the Association are:}

  \chadded[id=CAP3-Community-Shed]{The dominant purpose of the Association is to advance mental health and prevent or relieve social isolation.}

  \chadded[id=CAP3-Community-Shed]{The Association pursues this purpose by encouraging and facilitating creative use of technology at the Association's physical premises, where the Association supports individuals to undertake activities, or work on projects, in the company of others.}
  
  \chadded[id=CAP3-Community-Shed]{The objects of the Association, which fulfil its purpose, are to:}


    \begin{itemize}
    \item promote the creative use of technology;
    \item establish, maintain, and equip a shared work space for its members; \chcomment[id=RC]{Is this broad enough to cover purchasing, maintaining and repairing equipment and materials?}
    \item provide work space, storage, and other resources for the creative and artistic use of technology;
    \item foster a collaborative, inclusive, safe, and creative environment for artistic and technological projects;
    \item educate and train its members in skills relevant to its objects;
    \item organise educational, social and cultural events to promote the creative use of technology;
    \item raise funds to support its other objects;
    \item communicate and collaborate with others with similar objectives.
    \end{itemize}
  
  \item \textbf{Quorum for general meetings:} \label{key-info-quorum-for-general-meetings}
  
  Any 20\% of the ordinary members (being members entitled to vote under these rules at a general meeting) will constitute a quorum for the conduct of business at a general meeting.

  \item \textbf{Quorum for committee meetings:} \label{key-info-quorum-for-committee-meetings}
  
  Any 4 committee members constitute a quorum for the conduct of the business of a committee meeting.

  \item \textbf{Financial year:} \label{key-info-financial-year}
  
  The Association's financial year will be the period of 12 months commencing on 1st July and ending on 30th June of each year.

\end{enumerate}

\end{document}