\documentclass[../constitution.tex]{subfiles}
\begin{document}

\hypertarget{part-7-financial-matters}{%
\part{FINANCIAL MATTERS}\label{part-7-financial-matters}}

\hypertarget{source-of-funds}{%
\subsection{Source of funds}\label{source-of-funds}}

The funds of the Association may be derived from entrance fees, subscriptions, donations, fund-raising activities, grants, interest and any other sources approved by the committee.

\hypertarget{control-of-funds}{%
\subsection{Control of funds}\label{control-of-funds}}

\begin{enumerate}

\item The Association must open one or more accounts in the name of the Association with a financial institution from which all expenditure of the Association is made and into which all funds received by the Association are deposited.
\item Subject to any restrictions imposed at a general meeting, the committee may approve expenditure on behalf of the Association.
\item The committee may authorise the treasurer to expend funds on behalf of the Association up to a specified limit or specified purpose without requiring approval from the committee for each item on which the funds are expended.
\item All cheques, drafts, bills of exchange, promissory notes and other negotiable instruments of the Association must be signed by ---

  \begin{enumerate}
  
  \item 2 committee members; or
  \item one committee member and a person authorised by the committee.
  \end{enumerate}
\item All funds of the Association must be deposited into the Association's accounts within 10 working days after their receipt unless otherwise approved by the by-laws.
\end{enumerate}

\hypertarget{financial-statements-and-financial-reports}{%
\subsection{Financial statements and financial reports}\label{financial-statements-and-financial-reports}}

\begin{enumerate}

\item For each financial year, the committee must ensure that the requirements imposed on the Association under Part 5 of the Act relating to the financial statements or financial report of the Association are met. \label{committee-ensure-financial-requirements-met}
\item Without limiting subrule \ref{committee-ensure-financial-requirements-met}, those requirements include ---

  \begin{enumerate}
  
  \item if the Association is a tier 1 association, the preparation of the financial statements; and
  \item if the Association is a tier 2 association or tier 3 association, the preparation of the financial report; and
  \item if required, the review or auditing of the financial statements or financial report, as applicable; and
  \item the presentation to the annual general meeting of the financial statements or financial report, as applicable; and
  \item if required, the presentation to the annual general meeting of the copy of the report of the review or auditor's report, as applicable, on the financial statements or financial report.
  \end{enumerate}
\end{enumerate}

\note{

Notes for this rule: 

1. Under section 66 of the Act, an incorporated association must keep 
financial records that —  

(a) correctly record and explain its transactions and financial position and performance; and 

(b) enable true and fair financial statements to be prepared in accordance with Part 5 Division 3 of the Act. 

2. Under section 67 of the Act, an incorporated association must retain its financial records for at least 7 years after the transactions covered by the records are completed. 

}

\end{document}