\documentclass[../constitution.tex]{subfiles}
\begin{document}

\nonnumberedparts{Revision history}

This version of the constitution, based on the \href{https://www.commerce.wa.gov.au/consumer-protection/model-rules}{model rules} (Schedule 2 of the Regulations), was developed in committee meetings held 2018-08-19 and 2018-08-21, and initially adopted at the \href{https://wiki.artifactory.org.au/en/minutes/AGM/2018-09-15}{AGM held 2018-09-15.}

s\ref{member-rejoins-after-failing-to-pay-fee} was amended at the \href{https://wiki.artifactory.org.au/en/minutes/AGM/2022-09-17}{AGM held 2022-09-17}.

Major revisions were accepted unianimously at \href{https://wiki.artifactory.org.au/en/minutes/SGM/2022-03-04}{a special general meeting held 2023-03-04}, including:

\begin{itemize}
    \item Extensive proofreading corrections.
    \item Revised subrule \ref{member-cannot-vote-with-debts} regarding member eligibilty to vote at general meetings where the member owes money to the Association.
    \item Revised rule \ref{nomination-of-committee-members} regarding \textit{Nomination of committee members} to allow more flexible means for submitting nominations to the secretary.
    \item Significant changes to enable the Association to apply for Deductible Gift Recipient status in the "Community Shed" category.
          \begin{itemize}
              \item Revised the Association's purposes and objects, Key Information - Item \ref{key-info-objects-purposes}, to reflect the Association's alignment with the "Community Shed" category.
              \item Revised rules \ref{applying-for-membership} \textit{Applying for membership} and \ref{dealing-with-membership-applications} \textit{Dealing with membership applications} to provide for "open membership".
              \item Revised rule \ref{distribution-of-surplus-property-on-cancellation-of-incorporation-or-winding-up} regarding \textit{Distribution of surplus property on cancellation of incorporation or winding up} to meet ATO requirements for DGRs.
          \end{itemize}
    \item Restore provisions from the model rules which allow body corporates to be members of the Association.
    \item Revise rules \ref{notice-of-committee-meetings}, \ref{use-of-technology-to-be-present-at-committee-meetings} , \ref{notice-of-general-meetings}, and \ref{general-meeting-at-more-than-one-place} regarding committee meetings and general meetings which are held at more than one place e.g. electronically.
    \item Simplified rules \ref{quorum-for-committee-meetings} and \ref{presiding-member-and-quorum-for-general-meetings} regarding how long members should wait if not enough members are present to meet quorum requirements at a meeting.
    \item Clarify rule \ref{membership-fees} regarding \textit{Membership fees} to clarify how fees are set, and how members can be re-admitted if their membership lapses under subrule \ref{member-fails-to-pay-fee}.
    \item State under rule \ref{executing-documents} that the Association does not have a common seal.
    \item Rule \ref{emergency-disciplinary-actions} for \textit{Emergency temporary suspension} replaced by \textit{Emergency disciplinary actions}.
    \item Rules \ref{committee-members}, \ref{election-of-committee-members}, and \ref{election-of-office-holders} revised to clarify how committee members are elected, and how the committee members elect the office holders of the Association.
    \item Revise rule \ref{payments-to-committee-members} to allow payments to committee members for travel expenses under specific circumstances.
    \item Revise rule \ref{control-of-funds} so the Association can have more than one bank account.

\end{itemize}

A new clause \ref{free-and-sponsored-memberships-expire}, regarding when free and sponsored memberships cease, was added at the \href{https://wiki.artifactory.org.au/en/minutes/AGM/2023-09-16}{AGM held 2023-09-16}.

\end{document}